\documentclass[aspectratio=169]{beamer}

\title{SOLID React}
\author{Ethan Kent}
\institute{Spoonflower}
\date{\today}
\usetheme{Pittsburgh}

\begin{document}

\frame{\titlepage}

\begin{frame}

  \frametitle{SOLID Principles}

  \begin{description}
    \item[Single-Responsibility Principle] Functions (etc.) should have exactly
      one reason to change/be responsible to exactly one actor or stakeholder.
    \item[Open--Closed Principle] Functions (etc.) should be open for extension
      but closed for modification.
    \item[Liskov Substitution Principle] You should be able to replace a type
      with its subtype.
    \item[Interface-Segregation Principle] Code should not be required to rely
      on methods or properties it doesn't use.
    \item[Dependency-Inversion Principle] Functions (etc.) should depend on
      abstractions rather than concretions.
  \end{description}

\end{frame}

\begin{frame}

  \frametitle{Applying SOLID to React}

  \begin{itemize}
    \item Single-Responsibility Principle
          \begin{itemize}
            \item Separate logic from rendering.
            \item Consider volatility when designing shared code.
          \end{itemize}
    \item Open--Closed Principle
          \begin{itemize}
            \item Share code by composing rudimentary components; don't use
                  conditional logic to specialize a kitchen-sink component.
            \item Invert dependencies.
          \end{itemize}
    \item Liskov Substitution Principle
          \begin{itemize}
            \item Use TypeScript or strict type checking to ensure
                  compatibility.
          \end{itemize}
    \item Interface-Segregation Principle
          \begin{itemize}
            \item Avoid prop-drilling (also relevant to OCP).
            \item Avoid using optionality to facilitate polymorphism (also
                  relevant to OCP).
          \end{itemize}
    \item Dependency-Inversion Principle
          \begin{itemize}
            \item Use services/Onion Architecture to define props to allow
                  polymorphism (also relevant to OCP).
          \end{itemize}
  \end{itemize}

\end{frame}

\end{document}